Type Error Telemetry at Scale: Pseudonymized and Stochastic

### 2023-09-22 programming23/paper.tex
Minor edits

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains nine kinds of data:
record 
\begin{enumerate}
  \item metadata: a psedonymized session identifier, timestamp and session duration,
  \item mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item reason for sending: (random selection, or file switch),
  \item size of codebase: number of files, and number of lines of code type checked,
  \item size of edit range
  \item overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
    \FILL{} explain previous/current in detail, explain that this data takes up most of the telemetry record
  \item forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item TooComplexErrors: project-wide count for this one specific error type
\end{enumerate}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

There is a huge amount of variation across projects.
The largest ones have over 50k files (!) and 50k lines of code, and %50kLoC and 50k files????
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard deviations.
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
The high number of files may be because creators define many components to
build a Roblox experience and put these components in separate files.
(\FILL{} still that's a lot of components ... any better guesses?)

(\FILL{} doublecheck file sizes)
% That seems way off, not sure we're seeing so many files :/

@@

Similar to the data on project size, there is huge variation in session
length.
The longest sessions last several days and/or contain thousands of records,
while the shortest last a few milliseconds or include just one record.
Likewise, both plots in the figure follow a power-law distribution
(especially for record count).
A typical session runs on the order of minutes and consists of a few dozen events.
The median session time is approximately 14 minutes.
The median number of
records is 138.
These numbers are reasonable.

>>>>

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains nine kinds of data:
\begin{enumerate}
  \item metadata: a psedonymized session identifier, timestamp and session duration,
  \item mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item reason for sending: (random selection, or file switch),
  \item size of codebase: number of files, and number of lines of code type checked,
  \item size of edit range
  \item overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
    \FILL{} explain previous/current in detail, explain that this data takes up most of the telemetry record
  \item forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item TooComplexErrors: project-wide count for this one specific error type
\end{enumerate}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

There is a huge amount of variation across projects.
The largest ones have over 50,000 files, and
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard deviations.
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
One source of variation is that some developers use Luau scripts as a way
to store data, writing a module that exports one huge array, typically
defined on a single line. Such data storage scripts provide a challenge for
script tooling.

%% The high number of files may be because creators define many components to
%% build a Roblox experience and put these components in separate files.
%% (\FILL{} still that's a lot of components ... any better guesses?)

%% (\FILL{} doublecheck file sizes)
% That seems way off, not sure we're seeing so many files :/

@@

Similar to the data on project size, there is huge variation in session
length.
The longest sessions last several days and/or contain thousands of records,
while the shortest last a few milliseconds or include just one record.
Likewise, both plots in the figure follow a power-law distribution
(especially for record count).
A typical session runs on the order of minutes and consists of a few dozen events.
The median session time is approximately 14 minutes.
The median number of
records is 138.
% These numbers are reasonable.
